%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer} % Job title
    {Machine Learning Reply} % Organization
    {Milan, Italy} % Location
    {Jan. 2026 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Build agentic workflows, RAG pipelines, and LLM-powered automation for enterprise use cases, from prototyping through deployment.}
        \item {Deploy and operate generative-AI solutions on cloud infrastructure with containerized services and CI/CD.}
        \item {Apply evaluation and observability practices to keep AI systems reliable once exposed to real users and data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Fellow} % Job title
    {Imaging and Vision Laboratory (IVL), University of Milano-Bicocca} % Organization
    {Milan, Italy} % Location
    {Jan. 2025 - Dec. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Built a large-scale synthetic Side-Scan Sonar dataset of 20,000+ labeled images for underwater mine detection, exceeding the scale of existing public datasets.}
        \item {Applied and optimized super-resolution models (SPAN, DRCT) to recover detection performance comparable to high-resolution data.}
        \item {Trained lightweight YOLOv11n/s detectors for robust detection in low-visibility conditions; work received a Best Paper Award at ICIAP 2025.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
