%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Publications}

%---------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Co-Author} % Role
    {\href{https://proceedings.kr.org/2023/5/}{From Vision to Execution: Enabling Knowledge Representation and Reasoning in Hybrid Intelligent Robots Playing Mobile Games}} % Title
    {\href{https://kr.org/KR2023/}{KR2023}} % Location
    {Rhodes, Greece | September 2-8, 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{The paper explores the automation of interactions with touch surfaces, presenting a delta robot designed to engage in match-3 games and ball-sorting puzzles on mobile phones. This robot employs a vision module to identify objects by color and shape, and utilizes declarative models for decision-making based on game rules and strategies. By integrating AI techniques such as vision processing and answer set programming, the system simplifies motion control through its delta robot configuration. The authors detail the components of their robotic application, demonstrating its capabilities through implementations of various games. They suggest that this approach facilitates innovative combinations of knowledge representation and robotics, offering a controlled environment for experimenting with hybrid reasoning methods without the burden of technical implementation.}
        \item Keywords: Applications of KR in robotics, Applications of KR Integrating symbolic and sub-symbolic approaches, KR related tools and systems.
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Co-Author} % Role
    {An iterative abstraction and decision making pipeline for answer set programming in robots playing mobile games (submitted)} % Title
    {\href{https://www.iclp24.utdallas.edu/}{ICLP 2024}} % 
    {Dallas, Texas | 11-17 October, 2024} % 
    {
      \begin{cvitems} % Description(s)
        \item An extension of the paper \textit{"From Vision to Execution: Enabling Knowledge Representation and Reasoning in Hybrid Intelligent Robots Playing Mobile Games"}, providing a brief overview of the robot’s components, its runtime and design-time workflows, and its interactions with mobile phone games.
        \item Keywords: Applications of KR in robotics, Applications of KR Integrating symbolic and sub-symbolic approaches, KR related tools and systems.
      \end{cvitems}
    }



%---------------------------------------------------------
% Add more publications if you have them

\end{cventries}
